Verifying Demonstrations

### 2018-08-23 paper/privacy-properties.tex
Fixes label for witness-adv def, removes treated comment
Finalizes privacy properties

\daniel{The main idea is that the adversary cannot link the protester's real 
  identity \(P\) to the protest cause \cid.}

@@

Thus privacy remains.
For the protester we want unlinkability between a protester's real identity 
\(P\) and the cause identifier \(\cid\).
For the witness, we want unlinkability between a witness's identity \(W\) and a 
location \(l\).

\daniel{End of edits so far.}

>>>>

@@

Thus privacy remains.
For the protester we want unlinkability between a protester's real identity 
\(P\) and the cause identifier \(\cid\) against the adversary.
For the witness, we want unlinkability between a witness's identity \(W\) and a 
location \(l\) against the adversary.
To understand what unlinkability means in these two cases, we must consider the 
system and adversary model, which we will define next.

\daniel{I suggest ending here to continue in \cref{adversary-model}.}
